Reduced growth due to belowground sink limitation is not fully explained by reduced photosynthesis

### 2016-06-16 manuscript/manuscript_pve.Rmd
bm edits

\
The lack of detected shifts in partitioning to fine roots provides evidence against an optimal foraging strategy for seedlings in containers. It is instead possible that lateral root development is affected by inanimate obstacles and avoiding growth towards container walls may improve resource gain [@falik2005root]. The sensitivity of roots to their own exudates near obstructions may also prevent further growth [@semchenko2008foraging]. Here, we found that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space. Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning. Here, increases in SRL were detected in several of the soil volume treatments. This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect]. The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake. 
*add exudation*
Alternatively, root exudation may have increased with reduced rooting volumes to facilitate N uptake in favour of increasing partitioning to root biomass.

@@

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
**Figure 6**. (a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days. The dashed black line shows the 1:1 line and the dotted black line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling. (b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.

>>>>

\
The lack of detected shifts in partitioning to fine roots provides evidence against an optimal foraging strategy for seedlings in containers. It is instead possible that lateral root development is affected by inanimate obstacles and avoiding growth towards container walls may improve resource gain [@falik2005root]. Root exudation may have increased with reduced rooting volumes to facilitate N uptake in favour of increasing partitioning to root biomass. The sensitivity of roots to their own exudates near obstructions may also prevent further growth [@semchenko2008foraging]. Here, we found that FRLD was highest in smallest containers suggesting that root restriction likely occurred as simple function of available rooting space. Additionally, physical restriction of root proliferation could have impacted root development and morphology prior to shifts in mass partitioning. Here, increases in SRL were detected in several of the soil volume treatments. This is not surprising as plants in containers have been shown to have different root morphology to field grown plants [@nesmith1998effect]. The poor soil quality used in our experiment and root restriction, however, likely decreased the capacity of this morphological response to increase N uptake.

@@

```{r massmodel, fig.width=6, fig.height=8, echo=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/massmodel_optimize.R")
```  
**Figure 6**. (a) Total C mass of harvested seedlings versus modelled net leaf carbon gain over 120 days. The dashed black line shows the 1:1 line and the dotted blue line shows the seedling biomass that would be expected if all seedlings had the same carbon use efficiency as the freely grown seedling. (b) Ratio of final biomass to modelled net leaf C gain of plants growth in different container sizes.
